---
title: RStudio Customization's
author: Jacob Peterson
date: '2020-02-03'
slug: rstudio-customizations
categories:
  - R
  - Personal Configuration
tags:
  - RStudio
subtitle: ''
summary: 'This is my quick summary'
authors: []
lastmod: '2020-02-05T23:48:12-06:00'
featured: no
image:
  caption: ''
  focal_point: ''
  preview_only: no
projects: []
draft: true
output:
  blogdown::html_page:
    toc: yes
---

```{r, include=FALSE, echo=FALSE, eval=TRUE}
knitr::opts_chunk$set(echo=TRUE, eval=FALSE)
```

# Introduction

This is what I am going to teach

## Why I use GitHub

Description

## Software Requirements

All the software needed can be installed across all major operating systems (Linux, macOS X, and Microsoft Windows).

* **R** - 3.6.2

* **RStudio** - 1.3.776


# Global Options

Access the global options menu with **Tools** &rarr; **Global Options...**

### General &rarr; Basic

* Uncheck *'Restore .RData into workspace at startup'*
* Change *'Save workspace to .RData on exit'* to *'Never'*

### Code &rarr; Display

* Check '*Show line numbers*'
* Check '*Show margin*'

### Code &rarr; Saving
* Change '*Line dending conversion:'* to *'Posix (LF)'* to annoying whitespace errors switching between Windows and Unix computers

### Appearance

I found a neat package that has a lot of themes including the One Dark theme I use from the Atom Text Editor. Find it on GitHub at [gadenbuie/rsthemes](https://github.com/gadenbuie/rsthemes).

I found that you can edit the theme using the Rstudio API.

```{r}
#Install the package
devtools::install_github("gadenbuie/rsthemes")


#Install the themes
rsthemes::install_rsthemes()

#Apply the One Dark Theme
rstudioapi::applyTheme("One Dark {rsthemes}")
```

### Git/SVN

Check out my post on how to setup GitHub with RStudio [here]()

# Install Packages

```{bash}
sudo apt install default-jre default-jdk
sudo apt install libcurl4-openssl-dev libssl-dev libxml2-dev
sudo apt install gdal-bin python-gdal python3-gdal libgdal-dev
sudo apt install libproj-dev libgeos-dev libcairo2-dev
sudo apt install libudunits2-dev
```


```{bash}
sudo apt install texlive texlive-latex-extra lmodern
```

```{r}

# Oracle Java JDK  https://thishosting.rocks/install-java-ubuntu/ (java 11 linux uprising ppa version)
# install R (follow CRAN)
# install Rstudio (deb from Rstudio website)
# check if rJava will install might have to run: sudo R CMD javareconf

# #Install R packages
# install needed dependencies:
# Java Oracle Java JDK  https://thishosting.rocks/install-java-ubuntu/ (java 11 linux uprising ppa version)
# sudo add-apt-repository -y ppa:ubuntugis/ubuntugis-unstable
# sudo apt install gdal-bin python-gdal python3-gdal libgdal1-dev libgdal-dev
# sudo apt-get install libgdal1-dev libproj-dev libgeos-dev libcairo2-dev
# sudo apt-get install libudunits2-dev
# sudo apt-get install texlive texlive-latex-extra lmodern


packList <- c("lattice","sp","rgdal","rgeos","sf","data.table",
              "plyr","AICcmodavg","bbmle","devtools",
              "dismo","FactoMineR","fasterize","fields",
              "ggplotify","ggspatial","gtable","gridExtra",
              "maptools","reshape2","rJava","SDMTools","shiny",
              "spThin","survival","VGAM","raster",
              "tidyverse","tmap","tmaptools","devtools","captioner",
              "roxygen2","tidyverse","FNN","rmarkdown","blogdown","bookdown",
              "pagedown")

install.packages(packList)


#Personal Packages
devtools::install_github("jacpete/jpfxns")
devtools::install_github("jacpete/jpfxns2")


```



